\documentclass[11pt]{article}

\usepackage{graphicx}
\usepackage{framed}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}

\usepackage{booktabs}
\usepackage{amsmath}

\marginparwidth 0.5in 
\oddsidemargin 0.25in 
\evensidemargin 0.25in 
\marginparsep 0.25in
\topmargin 0.25in 
\textwidth=6in
\textheight=8in

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolor}{rgb}{0.95,0.95,0.95}

\lstset{
  backgroundcolor=\color{backcolor}, % Set background color
  commentstyle=\color{codegreen}, % Style for comments
  keywordstyle=\color{magenta}, % Style for keywords
  numberstyle=\tiny\color{codegray}, % Style for line numbers
  stringstyle=\color{codepurple}, % Style for strings
  basicstyle=\ttfamily\footnotesize, % Basic font style and size
  breakatwhitespace=false, % Don't break lines at whitespace only
  breaklines=true, % Enable line breaking
  captionpos=b, % Caption position (bottom)
  keepspaces=true, % Keep spaces
  numbers=left, % Show line numbers on the left
  numbersep=5pt, % Separation of numbers from code
  showspaces=false, % Don't show spaces as visible characters
  showstringspaces=false, % Don't show spaces in strings
  showtabs=false, % Don't show tabs as visible characters
  tabsize=2, % Tab size
  % language=Python % Specify the language
}

\begin{document}
\hfill\vbox{\hbox{Jude Shin}
		\hbox{CSC 321, Section 07}	
		\hbox{Module 09}	
		\hbox{\today}}\par

\bigskip
\centerline{\Large\bf Lab 8: Social Engineering \& Encrypted Emails}\par
\bigskip

This lab explores common security questions and how difficult they are to answer. It also explores the use of GNU Privacy Guard (GPG), and open source email encryption tool. As always, all the code can be found in our remote \href{https://github.com/jude-shin/CSC\_321}{GitHub repository}.


% ============================================================================

\section*{Task 1: Security Questions}
For this task, I chose the celebrity Taylor Swift

Taylor Swift

\begin{enumerate}
	\item What was the make and model of your first car? Lexus SC430
	\item What was the name of your elementary/primary school? The Wyndvroft School / West Reading Elementary Center, PA
	\item In what city or town does your nearest sibling live? (Austin Swift - Unknown)
	\item What time of the day were you born? (hh:mm) (Unclear) 05:17 am
	\item What is your pet’s name? (three cats) Meredith, Olivia, Benjamin
	\item In what year was your father born? 1952
	\item What is your favorite color? (Unknown)
	\item What was your favorite place to visit as a child? Christmas tree farm in hometown Wyomissing, PA
\end{enumerate}
\section*{Task 2: GNU Privacy Guard (GPG)}

\end{document}
